### 2014-07-15 ms/ms.Rmd
Add missing quotes

```{r,results="asis",echo=FALSE, message=FALSE}
library(plyr)
library(whisker)
details2B  <-  daply(data, .(studyName), function(x) studyDetails(x))
writeLines(details2B,sep="\n\n")
```

>>>>

```{r,results="asis",echo=FALSE, message=FALSE}
library(plyr)
library(whisker)

## for debugging
# for(s in unique(data$studyName)){
#  cat(s)
#  studyDetails(data[data$studyName==s,])}

details2B  <-  daply(data, .(studyName), function(x) studyDetails(x))
writeLines(details2B,sep="\n\n")
```
